---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

*comphy* is an R package accompanying the book This package accompanies the book  
[*Computational Physics with R*](https://iopscience.iop.org/book/mono/978-0-7503-2632-2).
It collects all the functions described and used throughout the book, providing ready-to-use implementations of numerical algorithms in computational physics.

The package includes routines for:

- Numerical differentiation and integration

- Solvers for ordinary differential equations

- Sturm–Liouville eigenvalue problems

- Monte Carlo methods

- Other algorithms relevant to physics and applied mathematics

## Installation
You can install the development version from GitHub with:

```{r echo=TRUE, eval=FALSE}
# install.packages("devtools")
devtools::install_github("jfoadi/comphy")
```
## Example
This is a simple example where a numerical derivative of sin(x) is computed using comphy:

```{r echo=TRUE, eval=TRUE}
library(comphy)

# Grid of known values
x <- seq(0,pi,length.out=11)

# Grid of values at which derivative must be calculated
# Same as x
x0 <- x

# Function known at tabulated points
f <- sin(x)+cos(x)

# Obtain a numerical derivative at those points
# using central differences (discard first and last value)
df <- deriv_reg(x0,x,f)

# Print derivative values
print(df)
```

The two `NA`'s are there because the derivative is calculated using a
centred difference.

## Documentation
All exported functions include documentation and usage examples.
For a comprehensive discussion and context, see the book
[*Computational Physics with R*](https://iopscience.iop.org/book/mono/978-0-7503-2632-2).

## License
GPL (>= 2)